A Lyapunov Analysis of Momentum Methods \\ in Optimization

### 2016-11-08 Draft14.tex
Update Draft14.tex

\subsection{The Quasi-Monotone Subgradient Method}
\label{Sec:QuasiMono}
The quasi-monotone subgradient method was developed by Nesterov~\cite{Nesterov15} as an alternative to the dual averaging method.  It also achieves the $O(1/\sqrt{k})$ lower bound for the class of methods with bounded subgradients. The advantage of the quasi-monotone method however is that a convergence-rate guarantee can be shown for the entire sequence of iterates instead of the average (or minimum) iterate, as is the case with the dual averaging method in the non-Euclidean setting. {\em We begin by studying the quasi-monotone method in the situation where we have full gradients, which we assume to be bounded} and show later how the analysis extends to the setting where we only have access to bounded subgradients. We also set the dual averaging term $\gamma_k \equiv 1$ for convenience and give an analysis of the full algorithm in Appendix~\ref{App:ProofQuasiGen}.  With these minor modifications, the algorithm can be understood as the explicit Euler method applied to~\eqref{Eq:Z} and the implicit Euler method applied to~\eqref{Eq:X} (where now, we take $e^{\beta_t} = A_{k+1}$, while leaving our identification for $\frac{d}{dt} e^{\beta_t}$ unchanged):

\begin{algorithm}[H]
\caption{The Quasi-Monotone (Sub)gradient Method $\gamma_k \equiv 1$}
{\bf Assumptions:} $f, h$ are convex and differentiable. $h$ is strongly-convex and $f$ has bounded gradients, $\sup_{x\in\X}\|\nabla f(x)\| = G <\infty$. \\
Let $A_0 = 1$, $x_0 = z_0$, $\tau_k = \frac{A_{k+1} - A_k}{A_{k+1}}$, $\alpha_k = A_{k} - A_{k-1}$ . Define recursively,
\begin{subequations}\label{Eq:QuasiSub1}
\begin{align}
x_{k+1} &= \tau_k z_k + (1 - \tau_k)x_{k} ,\label{Eq:ZSeqQuasi1}\\
z_k &= \arg \min_{z\in \X} \left\{ \sum_{i=1}^k \alpha_i \langle \nabla f(x_i), z\rangle + D_h(z, x_0)\right\} \label{Eq:XSeqQuasi1}.
\end{align} 
\end{subequations}
\end{algorithm}
\noindent This modified quasi-monotone subgradient method has optimality conditions
\begin{subequations}\label{Eq:QuasiSub}
\begin{align}
z_{k} &= x_{k} + \frac{A_{k+1}}{A_{k+1} -A_{k}} (x_{k+1} - x_k),\label{Eq:ZSeqQuasi}\\
\nabla h(z_{k+1}) -\nabla h(z_k) &= -(A_{k+1} - A_{k})\nabla f(x_{k+1})\label{Eq:XSeqQuasi}.
\end{align} 
\end{subequations}
%%%%%%%%%%%%%%%%%%%%%%% Estimate Sequences
%\noindent Notice,~\eqref{Eq:QuasiSub} can be interpreted as applying something akin to the explicit-Euler discretization to~\eqref{Eq:Z} instead of the implicit-discretization method~\eqref{Eq:ZSeq}. 
The following result illustrates how the discrete Lyapunov function~\eqref{Eq:DiscLyapFunc1} can be used to analyze~\eqref{Eq:QuasiSub}:
\begin{theorem}
\label{Thm:Quasi}
Using the Lyapunov function~\eqref{Eq:DiscLyapFunc1},
%\begin{equation}
%E_k = A_k (f(x_k) - f(x^\ast)) +  D_h(x^\ast, z_k)
%\end{equation}
we can show the quasi-monotone method~\eqref{Eq:QuasiSub} satisfies \[E_{k+1} - E_k \leq \,\,\varepsilon_k,\] where the error scales in the following way,%\footnote{For reference, the error for subgradient descent scales in the same way (see Appendix~\ref{App:MirrorDesc})}
\[\varepsilon_k = \frac{(A_{k+1}- A_k)^2}{2}\|\nabla f(x_{k+1})\|^2 \leq \frac{(A_{k+1}- A_k)^2}{2}G^2.\]
\end{theorem}
\noindent Taking $x = x^\ast$ and summing over $k$ results in the following convergence rate:
\begin{align}\label{Eq:BoundQuasi}
f(x_k) - f(x^\ast) \leq \frac{D_h(x^\ast , x_0) +A_0 (f(x_0) - f(x^\ast)) + \frac{1}{2}\sum_{i=0}^{k}\varepsilon_i }{A_k}.
\end{align}
If we optimize the bound~\eqref{Eq:BoundQuasi} over $A_k$, we can obtain an $O(1/\sqrt{k})$ convergence rate guarantee by setting a time-horizon for the algorithm to be run, and choosing $A_{k+1} - A_{k} =\frac{D_h(x,x_0)}{G\sqrt{k+1}}.$ Without this step, we suffer an additional $\log k$ factor in the the numerator.\footnote{See~\cite[2]{Nesterov15} for more details on this history on subgradient methods as well as step-size analysis.}

@@

\subsection{Other Discretizations}
We give examples of two other algorithms that are the result of discretizing the momentum dynamics~\eqref{Eq:DynaBeta}, and analyze them using the discretized Lyapunov function~\eqref{Eq:DiscLyapFunc1}. The proofs of these results can be found in the Appendix~\ref{App:OtherDiscret}. The first method is the result of applying the explicit Euler method to~\eqref{Eq:X} and the implicit Euler method to~\eqref{Eq:Z}:
\begin{algorithm}[H]
\caption{Method 1}
{\bf Assumptions:} $f$ is continuously differentiable, $\|\nabla^2 f\|\leq L$, and $\X$ is convex and compact. \\
Let $A_0 = 1$, $x_0 = z_0$, $\alpha_k = A_{k+1} - A_k$ and $\tau_k = \frac{A_{k+1}- A_k}{A_{k}}$. Define recursively,
\begin{subequations}\label{Eq:QuasiSub2}
\begin{align}
z_{k+1} &= \arg \min_{z \in \X} \left\{\langle \nabla f(x_k),z \rangle + \frac{1}{\alpha_k} D_h(z, z_k)\right\}\\
x_{k+1} &= \frac{\tau_k}{\tau_k - 1}z_{k+1} + \frac{1}{\tau_k - 1}  x_k
\end{align} 
\end{subequations}
\end{algorithm}
\noindent This algorithm has optimality conditions,
\begin{subequations}
\begin{align}
z_{k+1} &= x_{k+1} - \frac{A_{k}}{A_{k+1} -A_{k}} (x_{k+1} - x_k),\label{Eq:ZSeqOther1}\\
\nabla h(z_{k+1}) -\nabla h(z_k) &= -(A_{k+1} - A_{k})\nabla f(x_{k}) \label{Eq:XSeqOther1}.
\end{align}
\end{subequations}
\noindent Choosing $A_k = k(k+1)/2$ results in an $O(1/k)$ convergence rate. We remark that  this algorithm is structurally very similar to the conditional gradient method (see~\ref{App:OtherDiscret} for details). The second method does not correspond to a straightforward discretization technique and is given by the following sequences:
\begin{algorithm}[H]
\caption{Method 2}
{\bf Assumptions:} $f, h$ are convex and differentiable. $h$ is strongly-convex and $f$ has bounded gradients, $\sup_{x\in\X}\|\nabla f(x)\| = G <\infty$. 
Let $A_0 = 1$, $x_0 = z_0$ and $\tau_k = \frac{A_{k+1}- A_k}{A_{k}}$. Define recursively,
\begin{subequations}\label{Eq:QuasiSub3}
\begin{align}
x_{k+1}  &= \frac{\tau_k}{\tau_k + 1} z_k + \frac{1}{\tau_k+1}x_k,\\%\label{Eq:ZSeqQuasi}\\
z_{k+1} &= \arg \min_{z \in \X} \left\{\langle \nabla f(x_{k+1}),z\rangle + \frac{1}{\alpha_k} D_h(z, z_k)\right\}.
\end{align} 
\end{subequations}
\end{algorithm}
\noindent This algorithm has optimality conditions,
\begin{subequations}\label{Eq:QuasiSub3}
\begin{align}
z_{k} &= x_{k+1} + \frac{A_{k}}{A_{k+1} -A_{k}} (x_{k+1} - x_k),\label{Eq:ZSeqMethod2}\\%\label{Eq:ZSeqQuasi}\\
\nabla h(z_{k+1}) -\nabla h(z_k) &= -(A_{k+1} - A_{k})\nabla f(x_{k+1}).\label{Eq:XSeqMethod2}
\end{align} 
\end{subequations}
Notice, \eqref{Eq:QuasiSub3} is very similar to the quasi-monotone subgradient method~\eqref{Eq:QuasiSub1}. In particular, under the same assumptions, it achieves a $O(1/\sqrt{k})$ convergence rate. Furthermore, like the quasi-monotone subgradient method, it can be extended to functions which have bounded subgradients instead of full gradients and an additional weighting term can be added.

@@

We present two variants of the accelerated mirror descent algorithm (which is the accelerated gradient descent algorithm in the setting where $h = \frac{1}{2}\|\cdot \|^2$). Neither of these correspond to a straightforward discretization of~\eqref{Eq:EL}---they both entail introducing an additional sequence $\{y_k\}$ to obtain a better bound on the error. The first is the version introduced by Michel Baes~\cite{Baes09}:

@@

\quad M \|L^{-1} \nabla f(y_{k})\|_\ast^{2} &\leq L^{-1}\langle\nabla f(y_{k}), x_{k} - y_{k}\rangle \label{Eq:YSeqAcc3}

@@

As mentioned above, to obtain a convergence guarantee for both algorithms we have replaced the current state $x_k$ by another sequence $y_k$ which simply needs to satisfy~\eqref{Eq:YSeqAcc3}. Furthermore, we have replaced our sequence $A_{k+1}$ by $\tilde A_{k+1}$ which depends on the Lipschitz parameter. We make the same adjustments to the Lyapunov function~\eqref{Eq:DiscLyapFunc1} which we sum up in the following theorem:

@@

\[E_{k+1} - E_k \leq \varepsilon_k\]

@@

We choose $x = x^\ast$ and $A_k$ such that $\tilde A_{k+1}^{-1}(\tilde A_{k+1} -\tilde A_{k})^{2} \leq 2M$ to ensure the error is non-positive. With these choices, we obtain the following convergence rate,

@@

 The conditional Gradient Method, also called the {\em Frank-Wolfe} algorithm~\cite{FrankWolfe}, has garnered renewed interest over the last several years. This interest has inspired several different analyses~\cite{Freund14, Bach15} of the algorithm. Of particular note is the analysis provided by Nesterov~\cite{NesterovCond15}, who used to technique of estimate sequences to evaluate the algorithm under varying smoothness assumptions and step-size conditions. Nesterov also extended the algorithm to provide an analysis of a trust-region Newton-type method. Here, we explore the conditional gradient method from a dynamical view, and give an alternate analysis of both methods. To do so, we first revisit the derivation of the Lyapunov function. Notice, that if $\dot \beta_t >0 $ and we can ensure the following inequality for our dynamical system

@@

This algorithm has the following optimality conditions 

@@

In this section, we introduce a new family of momentum dynamics which can be discretized to obtain the accelerated gradient descent algorithm in the setting where the objective function $f$ is strongly convex. In Appendix~\ref{App:StrongConvexity}, we show how to derive a Lyapunov function using the dynamic. Furthermore, we show how to discretize the dynamics to obtain a discrete-time algorithm which can be analyzed by performing an analogous discretization of the Lyapunov function. 

@@

and use it to analyze the following dynamic, 

@@

We briefly remark that~\eqref{Eq:StrongDyn} is the Euler-Lagrange equation for the following Lagrangian,

@@

under the same ideal scaling conditions~\eqref{Eq:IdeSca}, where we take $e^{\alpha_t} = \dot \beta_t$. Furthermore, this Lagrangian can be generalized to include non-Euclidean geometries; however, further exploration of this Lagrangian is outside the scope of this work. Here, we demonstrate that~\eqref{Eq:StrongLyap} can be used to show an $O(e^{-\beta_t})$ rate of convergence for~\eqref{Eq:StrongDyn} with a strong convexity assumption. To do so, note that if we can ensure  $\dot \E_t = e^{\beta_t}\dot \beta_t \tilde{\E}_t + e^{\beta_t} \dot{\tilde{\E}}_t \leq 0$, which amounts to ensuring

@@

we obtain the following algorithm, 

@@

\varepsilon_k = \left(\frac{\tau_k^2}{2\mu} - \frac{1}{2L}\right)\|\nabla f(x_k)\|^2 + \left(\frac{\tau_kL}{2}-\frac{\mu}{2\tau_k}\right)\|x_k - y_k\|^2

@@

In this section, we connect our Lyapunov framework to the technique of estimate sequences.  We derive continuous-time estimate sequences directly from our Lyapunov function and demonstrate how these two techniques are equivalent in continuous and discrete time.

We begin with a brief reivew of the technique of estimate sequences. 
In \cite{Nesterov04}, Nesterov introduced estimate sequences by giving the following definition:
\begin{definition}\cite[2.2.1]{Nesterov04} A pair of sequences $\{\phi_k(x)\}_{k=1}^\infty$ and $\{A_k\}_{k=0}^\infty$ $A_k \geq1$ is called an {\em estimate sequence} of function $f(x)$ if 
\[ \frac{1}{A_k} \rightarrow 0 \]
and for any $x \in \R^n$ and all $k \geq 0$, we have 
\begin{equation}\label{Eq:Ineq1}
\phi_k(x) \leq \Big(1 - \frac{1}{A_k}\Big)f(x) + \frac{1}{A_k}\phi_0(x).
\end{equation}
\end{definition}
\noindent The following lemma, given by Nesterov, explains why estimate sequences are useful.
%
%
%Lemma 
\begin{lemma}\label{Lem:Nest2.2.1} \cite[2.2.1]{Nesterov04}
If for some sequence $\{x_k\}_{k\geq0}$ we have 
\begin{equation}\label{Eq:Seq}
f(x_k) \leq \phi_k^\ast \equiv \min_{x \in \X} \phi_k(x),
\end{equation}
then $f(x_k) - f(x^\ast) \leq \frac{1}{A_k} [\phi_0(x^\ast) - f(x^\ast)]$. 
\end{lemma}
%
%
\begin{proof}The proof is straightforward:
\begin{align*}
f(x_k) \overset{\eqref{Eq:Seq}}{\leq} \phi_k^\ast \equiv \min_{x \in \X} \phi_k(x) &\overset{\eqref{Eq:Ineq1}}{\leq}\min_{x \in\X}\left[\Big(1 - \frac{1}{A_k}\Big)f(x) + \frac{1}{A_k}\phi_0(x)\right]\\
&\leq \Big(1 - \frac{1}{A_k}\Big)f(x^\ast) + \frac{1}{A_k}\phi_0(x^\ast).
\end{align*}
Rearranging gives the desired inequality.
\end{proof}
%
%
Notice, this definition is not constructive and the definition of an estimation sequence is rather general. Finding sequences which satisfy these conditions is a non-trivial task. The next proposition, formalized by Baes in \cite{Baes09} as an  extension of Nesterov's Lemma 2.2.2 \cite{Nesterov04}, provides guidance for constructing estimate sequences. This construction is used in \cite{Nesterov04, Nesterov05, Nesterov08, Baes09, Nesterov15, NesterovCond15}, and is the only known way so far to construct an estimate sequence.  We will see below that this particular class of estimate sequences can be turned into our Lyapunov functions with a few algebraic manipulations (and vice-versa).
\begin{proposition}\cite[2.2]{Baes09}\label{Eq:Prop}
 Let $\phi_0: \X \rightarrow \R$ be a convex function such that $\min_{x \in \X} \phi_0(x)\geq f^\ast$. Suppose also that we have a sequence $\{f_k\}_{k\geq 0}$ of functions form $\X$ to $\R$ that underestimates $f$:
\begin{align}\label{Eq:Under}
f_k(x) \leq f(x) \quad \text{ for all $x \in \X$ and all $k \geq 0$}
\end{align}
Define recursively $A_0 = 1$ 
\begin{align}
\alpha_{k} &:= A_{k+1} - A_k \label{Eq:alpha}\\ 
\tau_k &:= \frac{a_{k}}{A_{k+1}},\label{Eq:tau}
\end{align}
and 
\begin{equation}\label{Eq:Est}
\phi_{k+1}(x) := (1 - \tau_k) \phi_k(x) + \tau_k f_k(x) = \frac{1}{A_{k+1}} \left(A_0\phi_0(x) + \sum_{i=0}^k a_i f_i(x)\right)
\end{equation}
for all $k\geq 0$. Then $\left(\{\phi_k\}_{k\geq0}, \{A_k\}_{k\geq0}\right)$ is an estimate sequence.
\end{proposition}
%\begin{remark}
%Going forth, we will denote the object
%\begin{equation}\label{Eq:Est2}
%\psi_k(x) := \sum_{i=0}^k a_i f_i(x) + \phi_0(x)
%\end{equation}
%as our estimate sequence.

>>>>

\subsection{The Quasi-Monotone Subgradient Method}
\label{Sec:QuasiMono}
The quasi-monotone subgradient method was developed by Nesterov~\cite{Nesterov15} as an alternative to the dual averaging method.  It also achieves the $O(1/\sqrt{k})$ lower bound for the class of methods with bounded subgradients. The advantage of the quasi-monotone method however is that a convergence-rate guarantee can be shown for the entire sequence of iterates instead of the average (or minimum) iterate, as is the case with the dual averaging method in the non-Euclidean setting. {\em We begin by studying the quasi-monotone method in the situation where we have full gradients, which we assume to be bounded} and show later how the analysis extends to the setting where we only have access to bounded subgradients. We also set the dual averaging term $\gamma_k \equiv 1$ for convenience and give an analysis of the full algorithm in Appendix~\ref{App:ProofQuasiGen}.  With these minor modifications, the algorithm can be understood as the explicit Euler method applied to~\eqref{Eq:Z} and the implicit Euler method applied to~\eqref{Eq:X} (where now we take $e^{\beta_t} = A_{k+1}$, while leaving our identification for $\frac{d}{dt} e^{\beta_t}$ unchanged):

\begin{algorithm}[H]
\caption{The Quasi-Monotone (Sub)gradient Method $\gamma_k \equiv 1$}
{\bf Assumptions:} $f, h$ are convex and differentiable. $h$ is strongly convex and $f$ has bounded gradients, $\sup_{x\in\X}\|\nabla f(x)\| = G <\infty$. \\
Let $A_0 = 1$, $x_0 = z_0$, $\tau_k = \frac{A_{k+1} - A_k}{A_{k+1}}$, $\alpha_k = A_{k} - A_{k-1}$ . Define recursively,
\begin{subequations}\label{Eq:QuasiSub1}
\begin{align}
x_{k+1} &= \tau_k z_k + (1 - \tau_k)x_{k} ,\label{Eq:ZSeqQuasi1}\\
z_k &= \arg \min_{z\in \X} \left\{ \sum_{i=1}^k \alpha_i \langle \nabla f(x_i), z\rangle + D_h(z, x_0)\right\} \label{Eq:XSeqQuasi1}.
\end{align} 
\end{subequations}
\end{algorithm}
\noindent This modified quasi-monotone subgradient method has optimality conditions
\begin{subequations}\label{Eq:QuasiSub}
\begin{align}
z_{k} &= x_{k} + \frac{A_{k+1}}{A_{k+1} -A_{k}} (x_{k+1} - x_k),\label{Eq:ZSeqQuasi}\\
\nabla h(z_{k+1}) -\nabla h(z_k) &= -(A_{k+1} - A_{k})\nabla f(x_{k+1})\label{Eq:XSeqQuasi}.
\end{align} 
\end{subequations}
%%%%%%%%%%%%%%%%%%%%%%% Estimate Sequences
%\noindent Notice,~\eqref{Eq:QuasiSub} can be interpreted as applying something akin to the explicit-Euler discretization to~\eqref{Eq:Z} instead of the implicit-discretization method~\eqref{Eq:ZSeq}. 
The following result illustrates how the discrete Lyapunov function~\eqref{Eq:DiscLyapFunc1} can be used to analyze~\eqref{Eq:QuasiSub}:
\begin{theorem}
\label{Thm:Quasi}
Using the Lyapunov function~\eqref{Eq:DiscLyapFunc1},
%\begin{equation}
%E_k = A_k (f(x_k) - f(x^\ast)) +  D_h(x^\ast, z_k)
%\end{equation}
we can show the quasi-monotone method~\eqref{Eq:QuasiSub} satisfies \[E_{k+1} - E_k \leq \,\,\varepsilon_k,\] where the error scales in the following way,%\footnote{For reference, the error for subgradient descent scales in the same way (see Appendix~\ref{App:MirrorDesc})}
\[\varepsilon_k = \frac{(A_{k+1}- A_k)^2}{2}\|\nabla f(x_{k+1})\|^2 \leq \frac{(A_{k+1}- A_k)^2}{2}G^2.\]
\end{theorem}
\noindent Taking $x = x^\ast$ and summing over $k$ results in the following convergence rate:
\begin{align}\label{Eq:BoundQuasi}
f(x_k) - f(x^\ast) \leq \frac{D_h(x^\ast , x_0) +A_0 (f(x_0) - f(x^\ast)) + \frac{1}{2}\sum_{i=0}^{k}\varepsilon_i }{A_k}.
\end{align}
If we optimize the bound~\eqref{Eq:BoundQuasi} over $A_k$, we can obtain an $O(1/\sqrt{k})$ convergence rate guarantee by setting a time-horizon for the algorithm to be run, and choosing $A_{k+1} - A_{k} =\frac{D_h(x,x_0)}{G\sqrt{k+1}}.$ Without this step, we suffer an additional $\log k$ factor in the the numerator.\footnote{See~\cite[2]{Nesterov15} for more details on this history on subgradient methods as well as step-size analysis.}

@@

\subsection{Other Discretizations}
We give examples of two other algorithms that are the result of discretizing the momentum dynamics~\eqref{Eq:DynaBeta}, and analyze them using the discretized Lyapunov function~\eqref{Eq:DiscLyapFunc1}. The proofs of these results can be found in the Appendix~\ref{App:OtherDiscret}. The first method is the result of applying the explicit Euler method to~\eqref{Eq:X} and the implicit Euler method to~\eqref{Eq:Z}:
\begin{algorithm}[H]
\caption{Method 1}
{\bf Assumptions:} $f$ is continuously differentiable, $\|\nabla^2 f\|\leq L$, and $\X$ is convex and compact. \\
Let $A_0 = 1$, $x_0 = z_0$, $\alpha_k = A_{k+1} - A_k$ and $\tau_k = \frac{A_{k+1}- A_k}{A_{k}}$. Define recursively,
\begin{subequations}\label{Eq:QuasiSub2}
\begin{align}
z_{k+1} &= \arg \min_{z \in \X} \left\{\langle \nabla f(x_k),z \rangle + \frac{1}{\alpha_k} D_h(z, z_k)\right\}\\
x_{k+1} &= \frac{\tau_k}{\tau_k - 1}z_{k+1} + \frac{1}{\tau_k - 1}  x_k.
\end{align} 
\end{subequations}
\end{algorithm}
\noindent This algorithm has optimality conditions,
\begin{subequations}
\begin{align}
z_{k+1} &= x_{k+1} - \frac{A_{k}}{A_{k+1} -A_{k}} (x_{k+1} - x_k),\label{Eq:ZSeqOther1}\\
\nabla h(z_{k+1}) -\nabla h(z_k) &= -(A_{k+1} - A_{k})\nabla f(x_{k}) \label{Eq:XSeqOther1}.
\end{align}
\end{subequations}
\noindent Choosing $A_k = k(k+1)/2$ results in an $O(1/k)$ convergence rate. We remark that  this algorithm is structurally very similar to the conditional gradient method (see~\ref{App:OtherDiscret} for details). The second method does not correspond to a straightforward discretization technique and is given by the following sequences:
\begin{algorithm}[H]
\caption{Method 2}
{\bf Assumptions:} $f, h$ are convex and differentiable. $h$ is strongly-convex and $f$ has bounded gradients, $\sup_{x\in\X}\|\nabla f(x)\| = G <\infty$. 
Let $A_0 = 1$, $x_0 = z_0$ and $\tau_k = \frac{A_{k+1}- A_k}{A_{k}}$. Define recursively,
\begin{subequations}\label{Eq:QuasiSub3}
\begin{align}
x_{k+1}  &= \frac{\tau_k}{\tau_k + 1} z_k + \frac{1}{\tau_k+1}x_k,\\%\label{Eq:ZSeqQuasi}\\
z_{k+1} &= \arg \min_{z \in \X} \left\{\langle \nabla f(x_{k+1}),z\rangle + \frac{1}{\alpha_k} D_h(z, z_k)\right\}.
\end{align} 
\end{subequations}
\end{algorithm}
\noindent This algorithm has optimality conditions,
\begin{subequations}\label{Eq:QuasiSub3}
\begin{align}
z_{k} &= x_{k+1} + \frac{A_{k}}{A_{k+1} -A_{k}} (x_{k+1} - x_k),\label{Eq:ZSeqMethod2}\\%\label{Eq:ZSeqQuasi}\\
\nabla h(z_{k+1}) -\nabla h(z_k) &= -(A_{k+1} - A_{k})\nabla f(x_{k+1}).\label{Eq:XSeqMethod2}
\end{align} 
\end{subequations}
Notice that \eqref{Eq:QuasiSub3} is very similar to the quasi-monotone subgradient method~\eqref{Eq:QuasiSub1}. In particular, under the same assumptions, it achieves a $O(1/\sqrt{k})$ convergence rate. Furthermore, like the quasi-monotone subgradient method, it can be extended to functions which have bounded subgradients instead of full gradients and an additional weighting term can be added.

@@

We present two variants of the accelerated mirror descent algorithm (which is the accelerated gradient descent algorithm in the setting where $h = \frac{1}{2}\|\cdot \|^2$). Neither of these correspond to a straightforward discretization of~\eqref{Eq:EL}---they both entail introducing an additional sequence $\{y_k\}$ to obtain a better bound on the error. The first is the version introduced by Baes~\cite{Baes09}:

@@

\quad M \|L^{-1} \nabla f(y_{k})\|_\ast^{2} &\leq L^{-1}\langle\nabla f(y_{k}), x_{k} - y_{k}\rangle. \label{Eq:YSeqAcc3}

@@

As mentioned above, to obtain a convergence guarantee for both algorithms we have replaced the current state $x_k$ by another sequence $y_k$ which needs to satisfy~\eqref{Eq:YSeqAcc3}. Furthermore, we have replaced our sequence $A_{k+1}$ by $\tilde A_{k+1}$ which depends on the Lipschitz parameter. We make the same adjustments to the Lyapunov function~\eqref{Eq:DiscLyapFunc1} which we summarize in the following theorem:

@@

\[E_{k+1} - E_k \leq \varepsilon_k,\]

@@

We choose $x = x^\ast$ and $A_k$ such that $\tilde A_{k+1}^{-1}(\tilde A_{k+1} -\tilde A_{k})^{2} \leq 2M$ to ensure the error is nonpositive. With these choices, we obtain the following convergence rate,

@@

 The conditional gradient method, also called the \emph{Frank-Wolfe} algorithm~\cite{FrankWolfe}, has garnered renewed interest over the last several years. This interest has inspired several different analyses~\cite{Freund14, Bach15} of the algorithm. Of particular note is the analysis provided by Nesterov~\cite{NesterovCond15}, who used to technique of estimate sequences to evaluate the algorithm under varying smoothness assumptions and step-size conditions. Nesterov also extended the algorithm to provide an analysis of a trust-region Newton-type method. Here, we explore the conditional gradient method from a dynamical view, and give an alternate analysis of both methods. To do so, we first revisit the derivation of the Lyapunov function. Notice, that if $\dot \beta_t >0 $ and we can ensure the following inequality for our dynamical system

@@

This algorithm has the following optimality conditions: 

@@

In this section, we introduce a new family of momentum dynamics which can be discretized to obtain the accelerated gradient descent algorithm in the setting where the objective function $f$ is strongly convex. In Appendix~\ref{App:StrongConvexity}, we show how to derive a Lyapunov function using the momentum dynamics. Furthermore, we show how to discretize the dynamics to obtain a discrete-time algorithm which can be analyzed by performing an analogous discretization of the Lyapunov function. 

@@

and use it to analyze the following dynamics: 

@@

Note that~\eqref{Eq:StrongDyn} is the Euler-Lagrange equation for the following Lagrangian:

@@

under the same ideal scaling conditions~\eqref{Eq:IdeSca}, where we take $e^{\alpha_t} = \dot \beta_t$. Furthermore, this Lagrangian can be generalized to include non-Euclidean geometries; however, further exploration of this Lagrangian is outside the scope of this work. Here, we demonstrate that~\eqref{Eq:StrongLyap} can be used to establish an $O(e^{-\beta_t})$ rate of convergence for~\eqref{Eq:StrongDyn} with a strong convexity assumption. To do so, note that if we can ensure  $\dot \E_t = e^{\beta_t}\dot \beta_t \tilde{\E}_t + e^{\beta_t} \dot{\tilde{\E}}_t \leq 0$, which amounts to ensuring

@@

we obtain the following algorithm:

@@

\varepsilon_k = \left(\frac{\tau_k^2}{2\mu} - \frac{1}{2L}\right)\|\nabla f(x_k)\|^2 + \left(\frac{\tau_kL}{2}-\frac{\mu}{2\tau_k}\right)\|x_k - y_k\|^2,

@@

In this section, we connect our Lyapunov framework directly to the technique of estimate sequences.  We derive continuous-time estimate sequences directly from our Lyapunov function and demonstrate how these two techniques are equivalent in continuous and discrete time.

We begin with a brief review of the technique of estimate sequences. 
In \cite{Nesterov04}, Nesterov introduced estimate sequences by giving the following definition:
\begin{definition}\cite[2.2.1]{Nesterov04} A pair of sequences $\{\phi_k(x)\}_{k=1}^\infty$ and $\{A_k\}_{k=0}^\infty$ $A_k \geq1$ is called an {\em estimate sequence} of function $f(x)$ if 
\[ \frac{1}{A_k} \rightarrow 0 \]
and for any $x \in \R^n$ and all $k \geq 0$, we have 
\begin{equation}\label{Eq:Ineq1}
\phi_k(x) \leq \Big(1 - \frac{1}{A_k}\Big)f(x) + \frac{1}{A_k}\phi_0(x).
\end{equation}
\end{definition}
\noindent The following lemma, given by Nesterov, explains why estimate sequences are useful.
%
%
%Lemma 
\begin{lemma}\label{Lem:Nest2.2.1} \cite[2.2.1]{Nesterov04}
If for some sequence $\{x_k\}_{k\geq0}$ we have 
\begin{equation}\label{Eq:Seq}
f(x_k) \leq \phi_k^\ast \equiv \min_{x \in \X} \phi_k(x),
\end{equation}
then $f(x_k) - f(x^\ast) \leq \frac{1}{A_k} [\phi_0(x^\ast) - f(x^\ast)]$. 
\end{lemma}
%
%
\begin{proof}The proof is straightforward:
\begin{align*}
f(x_k) \overset{\eqref{Eq:Seq}}{\leq} \phi_k^\ast \equiv \min_{x \in \X} \phi_k(x) &\overset{\eqref{Eq:Ineq1}}{\leq}\min_{x \in\X}\left[\Big(1 - \frac{1}{A_k}\Big)f(x) + \frac{1}{A_k}\phi_0(x)\right]\\
&\leq \Big(1 - \frac{1}{A_k}\Big)f(x^\ast) + \frac{1}{A_k}\phi_0(x^\ast).
\end{align*}
Rearranging gives the desired inequality.
\end{proof}
%
%
Notice, this definition is not constructive and the definition of an estimation sequence is rather general. Finding sequences which satisfy these conditions is a non-trivial task. The next proposition, formalized by Baes in \cite{Baes09} as an  extension of Nesterov's Lemma 2.2.2 \cite{Nesterov04}, provides guidance for constructing estimate sequences. This construction is used in \cite{Nesterov04, Nesterov05, Nesterov08, Baes09, Nesterov15, NesterovCond15}, and is the only known way so far to construct an estimate sequence.  We will see below that this particular class of estimate sequences can be turned into our Lyapunov functions with a few algebraic manipulations (and vice-versa).
\begin{proposition}\cite[2.2]{Baes09}\label{Eq:Prop}
 Let $\phi_0: \X \rightarrow \R$ be a convex function such that $\min_{x \in \X} \phi_0(x)\geq f^\ast$. Suppose also that we have a sequence $\{f_k\}_{k\geq 0}$ of functions form $\X$ to $\R$ that underestimates $f$:
\begin{align}\label{Eq:Under}
f_k(x) \leq f(x) \quad \text{ for all $x \in \X$ and all $k \geq 0$}
\end{align}
Define recursively $A_0 = 1$ 
\begin{align}
\alpha_{k} &:= A_{k+1} - A_k \label{Eq:alpha}\\ 
\tau_k &:= \frac{a_{k}}{A_{k+1}},\label{Eq:tau}
\end{align}
and 
\begin{equation}\label{Eq:Est}
\phi_{k+1}(x) := (1 - \tau_k) \phi_k(x) + \tau_k f_k(x) = \frac{1}{A_{k+1}} \left(A_0\phi_0(x) + \sum_{i=0}^k a_i f_i(x)\right)
\end{equation}
for all $k\geq 0$. Then $\left(\{\phi_k\}_{k\geq0}, \{A_k\}_{k\geq0}\right)$ is an estimate sequence.
\end{proposition}
%\begin{remark}
%Going forth, we will denote the object
%\begin{equation}\label{Eq:Est2}
%\psi_k(x) := \sum_{i=0}^k a_i f_i(x) + \phi_0(x)
%\end{equation}
%as our estimate sequence.
